---
title: "Wrack_monitoring_surveys"
author: "Ric DeSantiago"
date: "2023-01-30"
output: html_document
---

# Library
```{r}
library(knitr)
library(jtools)
library(tidyverse)
library(tidyr)
library(ggplot2)
library(ggfortify)
library(lme4)
library(car)
library(nlme)
library(ggpubr)
library(multcompView)
library(boot)
library(Hotelling)
library(mvnTest)
library(vegan)
library(factoextra)
library(FactoMineR)
library(agricolae)
library(glmm)
library(HH)
library(ggpubr)
library(rstatix)
#hi
```

#explore data
## wrack line surveys
```{r}
#upload data 
Wrack <- read.csv("wrack_line_survey.csv") 
Wrack<-subset(Wrack, !year== "2020")
view(Wrack)
wrackfig<- ggplot(Wrack, aes(x = site, y = percent, fill = sarg )) + geom_boxplot()
wrackfig
```

#
```{r}
Data<-read.csv("wrack_line_survey.csv",header=T)

View(Data)

Pie_data_RedEye<-subset(Data, site =="Red Eye")

view(Pie_data_RedEye)

Pie_data_Tranquil<-subset(Data, site == "Tranquil")

view(Pie_data_Tranquil)

Pie_data_Tender<-subset(Data, site =="Tender Beach")

View(Pie_data_Tender)

Pie_data_Artist<-subset(Data, site =="Artist")

View(Pie_data_Artist)

Pie_data_Bachelor<-subset(Data, site =="Bachelor")

View(Pie_data_Bachelor)

Pie_data_Cosign<-subset(Data, site =="Cosign")

View(Pie_data_Cosign)

Pie_data_Marker<-subset(Data, site =="W_Marker_Poles")

View(Pie_data_Marker)

Pie_data_Cissy<-subset(Data, site =="Cissy")

View(Pie_data_Cissy)





